---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# immor

<!-- badges: start -->
<!-- badges: end -->

immor ("immobilier" + "R", sounds like "immortal") scrapes real estate
listings from Swiss property portals, normalizes them into a 28-column
tibble, and provides type-safe deduplication. Designed as the data
engine behind
[blockr.immor](https://github.com/Layalchristine24/blockr.immor).

## Installation

You can install the development version of immor from
[GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("Layalchristine24/immor")
```

## Usage

```{r, eval = FALSE}
library(immor)

# Fetch listings from all portals
listings <- immor_fetch(immor_query())

# Inspect the result
dplyr::glimpse(listings)              # 28-column schema with types and sample values
head(listings$title)                  # listing titles
table(listings$portal)                # count per portal: "flatfox", "weckaeby"
table(listings$transaction_type)      # "rent" vs "buy"
table(listings$transaction_type, listings$portal)  

# Filter by portal or transaction type
listings |> dplyr::filter(portal == "weckaeby")
listings |> dplyr::filter(transaction_type == "rent")

# Check distinct values before filtering
dplyr::distinct(listings, portal)
dplyr::distinct(listings, transaction_type)
```

## Visual Pipeline

For an interactive, no-code data pipeline UI, see the companion package
[blockr.immor](https://github.com/Layalchristine24/blockr.immor).

## Supported Portals

| Portal | Country | Method | Status |
|---|---|---|---|
| flatfox.ch | Switzerland | REST API | Available |
| weck-aeby.ch | Switzerland | HTML scraping (CasaWP) | Available |

Most major Swiss portals (homegate, immoscout24, comparis, newhome,
properstar) use bot protection (DataDome/Cloudflare) and cannot be
scraped. See `doc/portals.md` for the full investigation.
